Literature Review - Informal

### 2019-11-28 Literature Review/Literature Review - Informal/sample.tex
Included MPC section - must read

\usepackage{matlab-prettifier}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{float}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{algpseudocode}
\usepackage{algorithm}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage[margin=0.5in,letterpaper]{geometry}
\def\changemargin#1#2{\list{}{\rightmargin#2\leftmargin#1}\item[]}
\let\endchangemargin=\endlist 
\usepackage{listings}
\def\changemargin#1{\list{}{\leftmargin#1}\item[]}
\let\endchangemargin=\endlist
\title{Literature Review - Informal}

@@

\maketitle tableofcontents

@@

Multi Agent Dynamics considers the problem of mathematically modelling learning in Multi Agent
Systems (MAS). This model then serves to be able to predict the evolution of a learning system as
well as to understand the trajectory of learning. Typically, this looks at considering whether or
not the method is likely to converge towards a Nash equilibrium. This is generally a difficult
problem to solve \cite{ShohamMultiagentFoundations} for all but toy problems. To extend this
applicability into real world settings requires the study of stable equilbrium points;
\cite{Letcher2019DifferentiableMechanics} shows that the stable equilbrium and Nash equilibrium (NE)
are not necessarily the same and, in fact, argue that stable points are more informative than NEs.
Stability provides some guarantees against the stochastic nature of the environment since a stable
equilibrium will always be returned to even after perturbations. This extremely important in Safe
and Trusted AI as it provides guarantees against undesired behaviour in real world learning
environments.

>>>>

\usepackage{matlab-prettifier}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{float}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{csquotes}
\usepackage{algpseudocode}
\usepackage{algorithm}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage[margin=0.5in,letterpaper]{geometry}
\def\changemargin#1#2{\list{}{\rightmargin#2\leftmargin#1}\item[]}
\let\endchangemargin=\endlist 
\usepackage{listings}
\def\changemargin#1{\list{}{\leftmargin#1}\item[]}
\let\endchangemargin=\endlist
\title{Literature Review - Informal}

@@

\maketitle

\tableofcontents

@@

\section{Stochastic and Robust Model Predictive Control}

\textbf{Francesco: I've moved this to the top for your attention - it seems to be the most
interesting problem with the scope to improve the theoretical results as well as applications in
complex domains which are of significant interest these days.}

The idea of Stochastic Control is best described in the research statement of the Control and
Analysis of Stochastic Systems (CASS) group at Penn State:

\begin{displayquote}
	"...to model, predict and control uncertain engineering systems where the interplay between
	dynamics and uncertainty (stochasticity) is important."
\end{displayquote}

When operating in the real world, systems are subject to uncertainty and environment perturbations.
Despite this, for their safe operation, they must provide certain guarantees (such as collision
avoidance) and remain stable. It is with this in mind that we must design control mechanisms for the
system which satisfy these requirements, even in the face of uncertainty. Methods in stochastic
control have found their way into controlling power distribution, chemical processes and (of course)
robotics.

Model Predictive Control is a long standing paradigm in AI which looks specifically at the problem
of operating real-world agents safely in the face of environmental disturbances. The overarching
idea begins with the assumpion that we have a model of the environment. As an example, in
the case of autonomous vehicles, we have a model of how adjusting the angle of the front wheels will
affect the heading of the car. We then perform a finite horizon look ahead, in which we estimate the
environment state for a few time steps ahead, and generate a policy for this horizon. The agent
performs the immediate action generated by the policy, and then we repeat the process, after taking
measurements of the environment to determine the error in the system. Throughout this process, the
controller (a.k.a. policy) must remain stable, but also satisfy constraints. From our previous
example, a likely constraint would be that the controller will never result in the car going on the
pavement, where it would present a real hazard to pedestrians. It is through these constraints, and
the requirement of stability that the system is required to remain safe throughout operation. To
that end, mathematical proofs of these properties are provided in the literature ensuring that we
can trust in the system's performance.

Deterministic MPC assumes that the environment is completely deterministic and, therefore, assumes
knowledge of the exact nature of the disturbances. This somewhat naive assumption simplifies
computation and so appears often in the literature, as in \cite{Rosolia2018}. However, it does not
provide strong guarantees outside of games and simulations. Robust MPC brings this to a higher level
of abstraction in which system perturbations, though deterministic, lie on a bounded set. Therefore,
we no longer assume the exact nature of the environment and can guard against worst case scenarios.
This is extremely effective in closed environments or for simple tasks, but falters in more complex
environments.

Stochastic Model Predictive Control (SMPC) lifts the assumption made in MPC, namely that
perturbations are deterministic and lie on a bounded set \cite{Mesbah2016}. To accomplish this, we
define chance constraints, for which probabilistic guarantees must be determined. Furthermore,
optimality is defined in terms of the minimisation of the expectation of a probabilistic
cost function. This formulation brings about controllers which are more applicable and robust when
deployed. However, the field is in its infancy and presents a number of theoretical challenges.
These are best described by Mesbah in \cite{Mesbah2016}

\begin{itemize}
	\item The arbitrary form of the feedback control laws
	\item The non-convexity and intractability of the chance constraints
	\item The complexity of the uncertainty propagations
	\item Establishing stability of the control problem
\end{itemize}

Since the review was written in 2016, there have been a number of approaches towards solving some of
these problems, most notably the intractability of the chance contraints. For instance, in 
\cite{Paulson2019}, Paulson and Mesbah propose the use of joint chance constraints in considering
time varying stochastic disturbances as well as model uncertainty. This is shown to be strongly
suited to non-linear systems, which itself is an open problem in the MPC sphere.

The problem of MPC, both in the stochastic, and the robust sense, are rife for work in theoretical
and applied problems. Control in autonomous systems is also one of the more applicable problems
related to STAI since it requires that we place mathematical guarantees on the performance and
stability of the system as well as guarantees on the satisfaction of constraints. This is, of
course, an ever present problem in autonomous systems which operate in the real world. I begin by
listing the more theoretical areas for exploration in MPC before then considering their application
domains.

\begin{itemize}
	\item Significant exploration is required with regards to the optimisation problem. Especially
	for non-linear (or coupled systems), solving the optimisation problem is a struggle. As such,
	approximate methods (such as sampling) should be explored and their effect on the system
	guarantees presented.
	\item Uncertainty propagation in SMPC is also an important problem since we must be able to
	determine the uncertainty in the environment model in order to generate control laws. We should
	consider a comparison of formal techniques, such as Bayesian inference (e.g. Markov models) or
	particle filters, against modern deep learning methods for propagation.
	\item Adaptive MPC is particularly important when considering failures in a system. In his talk,
	Mark Cannon considers the platooning problem (in which multiple autonomous vehicles move
	together whilst maintaining a specified distance from one another). Consider, then, the case
	where one vehicle undergoes a fault (burst tyre etc). The system model must incorporate this,
	and hence requires adaptation. It would again be interesting to consider the use of neural
	networks in this manner. However, specifically we should consider whether the use of a function
	approximator in the form of an NN might result in a violation of the constraints.
	\item Distributed predictive control. This is what, in my view, we could work towards. This is a
	difficult problem due to the coupled nature of the system dynamics. We will need to consider: the
	effect that each agent has on the other, the effect of the environment on all agents, estimating the
	future behaviour of each agent, and ensuring that all agents do not violate the constraints. It is
	here that I believe game-theoretic notions (especially differential games) will come to our
	aid. Similarly, mean-field games should be considered in the general N-agent problem, as well as
	in the case of multiple disturbances, but I will elaborate on this in the applied problems
	section.
\end{itemize}

\section*{Multi Agent Dynamics}

Multi Agent Dynamics considers the problem of mathematically modelling learning in Multi Agent
Systems (MAS). This model then serves to be able to predict the evolution of a learning system as
well as to understand the trajectory of learning. Typically, this looks at considering whether or
not the method is likely to converge towards a Nash equilibrium. This is generally a difficult
problem to solve \cite{ShohamMultiagentFoundations} for all but toy problems. To extend this
applicability into real world settings requires the study of stable equilbrium points;
\cite{Letcher2019DifferentiableMechanics} shows that the stable equilbrium and Nash equilibrium (NE)
are not necessarily the same and, in fact, argue that stable points are more informative than NEs.
Stability provides some guarantees against the stochastic nature of the environment since a stable
equilibrium will always be returned to even after perturbations. This extremely important in Safe
and Trusted AI as it provides guarantees against undesired behaviour in real world
environments.
